Type Classes for Mathematics in Type Theory

### 2010-06-28 jar.tex

In the absence of type classes, these are all very real problems, and for this reason the two biggest formalizations of abstract algebraic structures in Coq today (namely CoRN\cite{C-corn} and Ssreflect\cite{Packed}), both use \emph{bundled} representation schemes, using records with one or more of the components as fields instead of parameters. For reflexive relations, the following is a fully bundled representation---the other end of the spectrum:
\begin{lstlisting}
  Record ReflexiveRelation: Type :=
    { rr_carrier: Type
    ; rr_rel: relation rr_carrier
    ; rr_proof: Π x, rr_rel x x }.
\end{lstlisting}
Superficially, this instantly solves the problems described above: reflexive relations can now be declared and passed as self-contained packages, and the \lstinline|rr_rel| projection now constitutes a ``canonical name'' for relations that are known to be reflexive, and we could bind a notation to it. While there is no conventional notation for reflexive relations, the situation is the same in the context of, say, a semiring, where we would bind ``$+$'' and ``$*$'' notations to the record field projections for the addition and multiplication operations, respectively.

>>>>

In the absence of type classes, these are all very real problems, and for this reason the two biggest formalizations of abstract algebraic structures in Coq today, CoRN~\cite{C-corn} and Ssreflect~\cite{Packed}, both use \emph{bundled} representation schemes, using records with one or more of the components as fields instead of parameters. For reflexive relations, the following is a fully bundled representation---the other end of the spectrum:
\begin{lstlisting}
  Record ReflexiveRelation: Type :=
    { rr_carrier: Type
    ; rr_rel: relation rr_carrier
    ; rr_proof: Π x, rr_rel x x }.
\end{lstlisting}
Superficially, this instantly solves the problems described above: reflexive relations can now be declared and passed as self-contained packages, and the \lstinline|rr_rel| projection now constitutes a ``canonical name'' for relations that are known to be reflexive, and we could bind a notation to it. While there is no conventional notation for reflexive relations, the situation is the same in the context of, say, a semiring, where we would bind ``$+$'' and ``$*$'' notations to the record field projections for the addition and multiplication operations, respectively.
